\documentclass[letterpaper,10pt,titlepage,draftclsnofoot,onecolumn]{IEEEtran}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{titling}

\usepackage{alltt}
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\def\name{Michael Elliott, Kiarash Teymoury, Liv Vitale}

\input{pygments.tex}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs444 ''operating systems'' files  filesystem I/O},
  pdftitle = {CS 444 Homework 2},
  pdfsubject = {CS 444 Homework 2},
  pdfpagemode = UseNone
}

\title{CS 444 Homework 4}
\author{Michael Elliott, Kiarash Teymoury, Liv Vitale}

\begin{document}

\section{Design Plan}

\par We planned to look to see how slobs work and are implemented in the Kernel. From there we will 
look to see what we can find as far as the best fit for it. We need to come up with something so if an space is available, the slob doesn't just allocate it.

\section{Version Control Log}

\begin{tabular}{l l l}\textbf{Detail}  & \textbf{Description}\\\hline
\href{https://github.com/elliomic/CS-444/commit/7395ac889572508fb893198084f6f89186e6cfa1}{7395ac8} &  Finished and submitted concurrency 5\\\hline

\href{https://github.com/elliomic/CS-444/commit/12acdee67ef6384d8f95e9899ff6ebbfd74de61e}{12acdee} & Added syscall header and table\\\hline

\href{https://github.com/elliomic/CS-444/commit/f264f4bb36821131ad6a4cad491bc88dd4368da9}{a71a217} & Updated Makefiles. Added LaTeX dependencies\\\hline

\href{https://github.com/elliomic/CS-444/commit/d8c088aa0b512484a45a62e2ffd0e0533d1cbf8d}{d8c088a} &Added Latex For Hw4.\\\hline

\href{https://github.com/elliomic/CS-444/commit/f651d37b2422b4ebd25687f7ac8c456b618ddb45}{f651d37} & Answered Concurency Questions\\\hline


\end{tabular}

\section{Work Log}
\begin{tabular}{l | c | r}
Date + Time & Item(s) worked on \\
\hline

\end{tabular}

\section{Concurrency Assignment}
\begin{enumerate}
\item \textbf{What do you think the main point of this assignment is?}

\par The main point of this assignment was to look into how memory management and system calls work.

\item \textbf{How did you personally approach the problem? Design decisions, algorithm, etc}

\par We wanted to figure out the best fit for the system calls. Therefore, we first figured them out and then found the best fit.

\item \textbf{How did you ensure your solution was correct? Testing details, for instance.}

\par If the vm booted up, we knew that we had the right solution. If it didn't, then it was wrong,

\item \textbf{What did you learn?}

\par We learned about memory management and system calls.

\end{enumerate}

\nocite{*}

\bibliography{test}
\bibliographystyle{plain}

\end{document}